\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-08-07 popl-2019-journal-v/paper.tex
[POPLjv] Relate to other notions of secure compilation

\dominique{TODO Relate full-abstraction to other notions of secure compilation}

@@

>>>>

@@

There are other notion of secure compilation than full-abstraction~\citep{abadi_protection_1998}.
\citet{abate_2019} presents an overview of trace-based secure compilation properties.
They show that full-abstraction is a weak notion of secure compilation relatively to other notions, e.g., Robust Relational Hyperproperty Preservation (RrHP) their strongest notion of secure compilation.
However, other notions of secure compilation that promise WBCF and LSE must also enforce it somehow.
\stktokens{} is an enforcement scheme that likely would work for stronger notions of secure compilation.
In fact, we believe that our result could be lifted from full-abstraction to RrHP reusing the back-translation from the full-abstraction proof.
